---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
 body {
  font-family: 'Roboto Condensed';
  background-color: #b0bf84;
  font-size: 20px;
}
h2 {
color: #34384b;
}
h3 {
color: #494078;
}

```

## Birds spotted around Tamaki Makaurau Auckland 
Tamaki Makaurau Auckland has many different species of birds present around the city. They inhabit many areas varrying from parks to peoples gradens. This report looks to log some of that diversity and present it in 2 easily digestable, and colourful, bar charts. 

```{r}
library(tidyverse)
library(magick)
## Importing our CSV
logged_data = read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTOEonK8ilXfFjpLMTf8cPizDb2dxFYK0E1Rz0ksfEI853XPSVR_cHIUxy15O1RdOcw0YydWk7CJsv4/pub?output=csv") %>%
  rename(Species = 2, Bird_number = 3, Native_or_not = 4)

## The total number of responses 
Total_survey = length(logged_data$Species)

## The total number of individual birds spotted within the survey
Total_bird_number = sum(logged_data$Bird_number)

```
### Data about the survey itself
- In total there were **`r Total_bird_number `** birds spotted through out all of the responses to the survey.
- In total to date there have been **`r Total_survey `** responses to the survey. 

### If you wish to fill out the survey yourself it can be found here:

[*Click here*](https://docs.google.com/forms/d/e/1FAIpQLSeDvUddI-7dkcU234_B1SEd_XedrnOpzu0s8k3h5mwloJVbiA/viewform?usp=dialog)

## Bar chart number 1:

``` {r,fig.height=5,fig.width=7}

## Plot to look at whether people know their native birds as compared to their non-native birds.The that colours fill the bars represent what the type of bird spotted was. 
Bar_chart1 = ggplot(aes(x = Native_or_not, fill= Species), data= logged_data) +geom_bar() +
            xlab("Nativness") +ylab("Number of times spotted") + 
          scale_fill_manual(values = c("#89afc6","#99a1b3", "#d97960","#928c5b","#c6d365","#2c2c2c","#415227","#656462","#bc844c"))

Bar_chart1

```

This chart compares the number of instances that people place a bird into comparing the natives to non-natives and to those that people don't know which category the species belongs too. The colours filling out the bars show which species make up that count in each of the columns. 

``` {r,fig.height=5,fig.width=8.75}
## Bar chart plotting out the different species spotted as compared to number of instances they were spotted in
Bar_chart2 =ggplot(aes(x=Species, fill = Species), data = logged_data) + geom_bar()+
            xlab("Type of bird") +ylab("Number of instances this species was spotted") + scale_fill_manual(values = c("#89afc6","#99a1b3", "#d97960","#928c5b","#c6d365","#2c2c2c","#415227","#656462","#bc844c"))
Bar_chart2
```

This chart compares all the different types of birds that were spotted during the survey as compared to the number of instances that each of these birds were spotted in. Each species, or bird type, has a different colour for their bar. 
